---
title       : Exploring mtCars Dataset
subtitle    : Developing Data Products - Course Project 
author      : Zarmeen Nasim
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## About

This project is developed as a part of Coursera Data Science Specialization - Developing Data Products Course.

My Shiny application https://zarmeen.shinyapps.io/Developing-Data-Products/ allows users to estimate the slope at which we can have minimum MSE i.e Mean Squared Error.

I have used mtcars Dataset available in R


--- .class #id 

## Dataset

```{r}
library(datasets)
head(mtcars)
```

--- .class #id
## Estimating Beta
My shiny app allow user to estimate beta that best fits the linear model between miles per gallon (mpg) and weight (wt) of car

Below code shows how we can get beta from lm function
```{r}
library(datasets)
fit <- lm(mpg ~ wt,data = mtcars)
fit

```

--- .class #id
## Plotting mtcars dataset

```{r echo=FALSE}
data("mtcars")
plot(mtcars$wt,mtcars$mpg,
xlab = "Weight(1000 lbs)",
ylab = "Miles per Gallon(mpg)",
bg = "lightblue",
col = "black", cex = 2, pch = 21,frame = TRUE)
abline(lm(mpg ~ wt,data = mtcars), lwd = 3)
```


--- .class #id
## Project Links
1. Github Repo
    https://github.com/zarmeen92/Developing-Data-Products
2. Shiny App
    https://zarmeen.shinyapps.io/Developing-Data-Products/
    